---
title: "Valence & Arousal: Analysis"
author: "A Garron Torres, Maia Rocklin, Nilam Ram"
date: '2023-07-20'
output:    
  rmdformats::robobook:
    gallery: TRUE
    lightbox: TRUE
editor_options: 
  chunk_output_fype: console
  chunk_output_type: console
---

```{=html}
<style type="text/css">
  body, html{
    font-family: Helvetica;
}
.book .book-body .page-inner section.normal h1{
  font-family: Source Sans Pro;
  font-weight: bold;
  color:#8c1515;
} 
.book .book-body .page-inner section.normal h2,
.book .book-body .page-inner section.normal h3, 
.book .book-body .page-inner section.normal h4{
  font-family: Source Sans Pro;
  font-weight: bold;
}

.book .book-body .page-inner section.normal table  td,
.book .book-body .page-inner section.normal pre>code.r,
.book .book-body .page-inner section.normal pre{
   font-family: Andale Mono;
}

</style>
```

# Set-Up

Note, DecTools mascks ICC and SD from the psych package. 

```{r setup, include = T, message=F, warning=F}

#Packages
library(tidyverse)       # data manipulation
library(psych)           # data descriptives
library(DescTools)       # Lin's Correspondance Coefficient
library(gt)              # table formatting
library(gtable)          # table formatting
library(gtsummary)       # table summaries
library(kableExtra)      # table formatting
library(knitr)           # html table formatting
library(irr)             # interrater reliabilities
library(stringr)         # work with strings
library(labelled)        # work with labels
library(lubridate)       # date formatting
library(viridis)         # color pallets 
library(plotly)          # 3D plots

#Set gt_theme for summary tables
theme_gtsummary_compact()

```

## Import Files

[Note on the OASIS file:]{.underline}

The OASIS study (Kurdi et al., 2017), human participants rated the images on a 1-7 likert scale. All subsequent machine and human ratings were done on a 1-9 likert scale.

</p>

The variables are denoted as follows:

-   "actual" OASIS vars (*actual_valence* & *actual_arousal*) were the participant rated OASIS images on a 1-7 scale.

-   "adjusted" OASIS values (*adjusted_valence* & *adjusted_arousal*) are the participant values adjusted to a 1-9 scale.

Kurdi, B., Lozano, S., & Banaji, M. R. (2017). Introducing the Open Affective Standardized Image Set (OASIS). Behavior Research Methods, 49(2), 457–470. https://doi.org/10.3758/s13428-016-0715-3

```{r file import, include=T, message=F, warning=F}

#Human Data
image_ratings_human_url <- "https://raw.githubusercontent.com/The-Change-Lab/affectivedynamics/main/data/image_ratings_human.csv"
image_ratings_human <- read.csv(file=url(image_ratings_human_url), header=T)

#All Ratings
image_ratings_all_url <- "https://raw.githubusercontent.com/The-Change-Lab/affectivedynamics/main/data/image_ratings_all.csv"
image_ratings_all <- read.csv(file=url(image_ratings_all_url), header=T)

#Day in the Life Deep Affect Modules (DAM)
image_ratings_DITL_url <- "https://raw.githubusercontent.com/The-Change-Lab/affectivedynamics/main/data/image_ratings_DITL.csv"
image_ratings_DITL <- read.csv(file=url(image_ratings_DITL_url), header=T)

```

## Reshape & Subset Files

Resphaping and subsetting files for later plotting & analysis.

```{r subset, warning=F, message=F}

#Ratings by source
image_ratings_smartphone <- image_ratings_all %>%
  filter(source == "smartphone")

image_ratings_OASIS <- image_ratings_all %>%
  filter(source == "OASIS")

#Long form valence ratings
valence_long <- image_ratings_all %>%
  select(image, valence_human, valence_ml, source) %>%
  pivot_longer(cols = c("valence_human", "valence_ml"),
               names_to = "raiter", 
               values_to = "valence") %>%
  mutate(raiter = ifelse(raiter == "valence_human", "human", "machine"))

#Long form arousal ratings
arousal_long <- image_ratings_all %>%
  select(image, arousal_human, arousal_ml, source) %>%
  pivot_longer(cols = c("arousal_human", "arousal_ml"),
               names_to = "raiter", 
               values_to = "arousal") %>%
  mutate(raiter = ifelse(raiter == "arousal_human", "human", "machine"))

#Long form ratings
image_ratings_all_long <- merge(valence_long, arousal_long, by = c("image", "raiter"))
image_ratings_all_long <- image_ratings_all_long %>%
  rename(source = source.x) %>%
  select(image, raiter, source, valence, arousal)

image_ratings_all_extralong <- image_ratings_all %>%
  select(image, arousal_human, arousal_ml, valence_human, valence_ml, source) %>%
  pivot_longer(cols = c("valence_human", "valence_ml", "arousal_human", "arousal_ml"),
               names_to = "raiter", 
               values_to = "value") %>%
  mutate(measure = gsub("_.*", "", raiter),
         raiter = gsub(".*_", "", raiter))

#DITL Label Images
image_ratings_DITL <- image_ratings_DITL %>%
  arrange(date) %>%
  mutate(row_id=row_number())

#DITL Long
image_ratings_DITL_long <- image_ratings_DITL %>%
  pivot_longer(cols = c("valence", "arousal"),
               names_to = "rating")

```

# Data Overview

## Source

```{r source, message=F, warning=F}

#Source
image_ratings_human %>%
  mutate(source = as_factor(source)) %>%
  select(source) %>%
  tbl_summary(
    label = list(source ~ "Source"),
    statistic = list(all_continuous() ~ "{mean} ({min}, {max})"),
    missing = "ifany") %>%
  modify_header(label ~ "") %>%
  as_gt() %>%
  tab_header("Valence & Arousal Survey Data") 

```

## Demographics

```{r demographics, message=F, warning=F}

#Basic Demographics
image_ratings_human %>%
  mutate(gender = factor(gender, 
                         levels=c(1,2,3,4,5),
                         labels=c("Male", "Female", "Non-binary", "Other", 
                                  "Prefer not to answer")),
         race = factor(race,
                       levels=c(1,2,3,4,5,6,7),
                       labels=c("White", "Native American", "Asian", "Black", "Other", 
                                  "Prefer not to answer", "Multiracial")),
         hispanic = factor(hispanic,
                           levels=c(1,2,3),
                           labels=c("Hispanic or Latino/Latina",
                                    "Not Hispanic or Latino/Latina",
                                    "I prefer not to answer"))) %>%
  select(age, gender, race, hispanic) %>%
  tbl_summary(
    label = list(age ~"Age", gender ~ "Gender", race ~ "Race", hispanic ~ "Hispanic"),
    statistic = list(all_continuous() ~ "{mean} ({min}, {max})"),
    missing = "ifany") %>%
  modify_header(label ~ "") %>%
  as_gt() %>%
  tab_header("Valence & Arousal Survey Data") 

#Expanded Demographics
image_ratings_human %>%
  mutate(education = factor(education,
                            levels=c(1,2,3,4,5,6,7,8),
                            labels=c("Less than high school", "Some college",
                                     "2-year college degree", "4-year college degree",
                                     "Master's degree", "Doctoral's degree",
                                     "Professional degree, e.g., JD/MD", 
                                     "High school/GED/Technical/vocational training)")),
         marital_status = factor(marital_status,
                                 levels=c(1,2,3,4),
                                 labels=c("Married, or living as married",
                                          "Divorced or separated",
                                          "Widowed",
                                          "Single/never married")),
         smartphone_hours = factor(smartphone_hours,
                                   levels=c(1,2,3,4,5),
                                   labels=c("0-1 hours", "1-3 hours",
                                            "3-5 hours", "5-7 hours",
                                            "More than 7 hours"))) %>%
  select(education, marital_status, smartphone_hours) %>%
  tbl_summary(
    label = list(education ~ "Education", 
                 marital_status ~ "Marital Status",
                 smartphone_hours ~ "Smartphone Hours"),
    statistic = list(all_continuous() ~ "{mean} ({min}, {max})"),
    missing = "ifany") %>%
  modify_header(label ~ "") %>%
  as_gt() %>%
  tab_header("Valence & Arousal Survey Data") 

```

## Polific Only Demographics

```{r prolific, warning=F, message=F}

#Prolific Only Demographics
image_ratings_human %>%
  filter(source == "prolific") %>%
  mutate(income = factor(income,
                         levels=c(1,2,3,4,5,6,7,8,9,10,11,12),
                         labels=c("$14,999 or less", "$15,000 - $24,999",
                                  "$25,000 - $29,999","$30,000 - $34,999",
                                  "$35,000 - $49,999", "$50,000 - $74,999",
                                  "$75,000 - $99,999", "$100,000 - $149,999",
                                  "$150,000 - $199,999", "$200,000 or more",
                                  "Don't know", "I prefer not to answer")),
         marital_status = factor(marital_status,
                                 levels=c(1,2,3,4),
                                 labels=c("Married, or living as married",
                                          "Divorced or separated",
                                          "Widowed",
                                          "Single/never married")),
         residence = factor(residence,
                            levels=c(1,2,3),
                            labels=c("Urban", "Suburban", "Rural")),
         region = factor(region, 
                         levels=c(1,2,3,4),
                         labels=c("Northeast", "South", "West", "Midwest"))) %>%
  select(marital_status, income, residence, region) %>%
  tbl_summary(
    label = list(income ~ "Income",
                 marital_status ~ "Marital Status",
                 residence ~ "Residence", region ~ "Region"),
    statistic = list(all_continuous() ~ "{mean} ({min}, {max})"),
    missing = "ifany") %>%
  modify_header(label ~ "") %>%
  as_gt() %>%
  tab_header("Valence & Arousal Survey Data") 

```

## Location

```{r location, warning=F, message=F}

#All students were attending suburban, west coast institutions
image_ratings_human <- image_ratings_human %>%
  mutate(residence_all = ifelse(source == "prolific", residence, 2),
         region_all = ifelse(source == "prolific", region, 3))

#Label factor levels
residence_relabel <- function(orig_data){
  val_labels(orig_data) <- 
    c("Urban" = 1, 
      "Suburban" = 2,
      "Rural" = 3
      ) 
  return(orig_data)
}

region_relabel <- function(orig_data){
  val_labels(orig_data) <- 
    c("Northeast" = 1, 
      "South" = 2,
      "West" = 3,
      "Midwest" = 4
      ) 
  return(orig_data)
}

image_ratings_human$residence_all <- residence_relabel(image_ratings_human$residence_all)
image_ratings_human$region_all <- region_relabel(image_ratings_human$region_all)

#Look at location summary
image_ratings_human %>%
  mutate(residence_all = as_factor(residence_all),
         region_all = as_factor(region_all)) %>%
  select(residence_all, region_all) %>%
  tbl_summary(
    label = list(residence_all ~ "Residence", region_all ~ "Region"),
    statistic = list(all_continuous() ~ "{mean} ({min}, {max})"),
    missing = "ifany") %>%
  modify_header(label ~ "") %>%
  as_gt() %>%
  tab_header("Valence & Arousal Survey Data") 
  
```

# Valence & Arousal Plots

## Valence Plots

```{r valence plots, warning=F, message=F}

#Valence Ratings
image_ratings_all %>%
  ggplot(aes(x = valence_human, y = valence_ml)) +
  geom_smooth(method = "lm", se = T, colour = "grey", linewidth = 0.5, alpha = 0.5) +
  geom_point(colour = "blue") +
  ggtitle("Valence") +
  scale_x_continuous("Human Ratings", limits = c(1,9), n.breaks = 9) +
  scale_y_continuous("ML Ratings", limits = c(1,9), n.breaks = 9) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) 

image_ratings_all %>%
  ggplot(aes(x = valence_human, y = valence_ml, color = source)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ggtitle("Valence") +
  scale_x_continuous("Human Ratings", limits = c(1,9), n.breaks = 9) +
  scale_y_continuous("Machine Ratings", limits = c(1,9), n.breaks = 9) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) 

```

## Arousal Plots

```{r arousal plots, warning=F, message=F}

#Arousal Ratings
image_ratings_all %>%
  ggplot(aes(x = arousal_human, y = arousal_ml)) +
  geom_smooth(method = "lm", se = T, colour = "grey", linewidth = 0.5, alpha = 0.5) +
  geom_point(colour = "red") +
  ggtitle("Arousal") +
  scale_x_continuous("Human Ratings", limits = c(1,9), n.breaks = 9) +
  scale_y_continuous("Machine Ratings", limits = c(1,9), n.breaks = 9) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

image_ratings_all %>%
  ggplot(aes(x = arousal_human, y = arousal_ml, color = source)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ggtitle("Arousal") +
  scale_x_continuous("Human Ratings", limits = c(1,9), n.breaks = 9) +
  scale_y_continuous("Machine Ratings", limits = c(1,9), n.breaks = 9) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

```

## Comparing Valence & Arousal

```{r valence vs arousal, warning=F, message=F}

#All by Rater
image_ratings_all_long %>%
  group_by(image) %>%
  ggplot(aes(x = arousal, y = valence, color = raiter)) +
  geom_point() +
  geom_line(aes(group = image), color="grey") +
  ggtitle("Valence and Arousal by Raiter") +
  scale_x_continuous("Arousal", limits = c(1,9), n.breaks = 9) +
  scale_y_continuous("Valence", limits = c(1,9), n.breaks = 9) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

image_ratings_all_long %>%
  group_by(image) %>%
  ggplot(aes(x = arousal, y = valence, color = raiter)) +
  geom_point() +
  geom_line(aes(group = image), color="grey") +
  ggtitle("Valence and Arousal by Raiter") +
  scale_x_continuous("Arousal", limits = c(1,9), n.breaks = 9) +
  scale_y_continuous("Valence", limits = c(1,9), n.breaks = 9) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  facet_wrap(~source)

```

## By Image Source

```{r plots source, warning=F, message=F}

#Arousal
image_ratings_all %>%
  group_by(source) %>%
  ggplot(aes(x = arousal_human, y = arousal_ml)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ggtitle("Arousal") +
  scale_x_continuous("Human Ratings", limits = c(1,9), n.breaks = 9) +
  scale_y_continuous("Machine Ratings", limits = c(1,9), n.breaks = 9) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  facet_wrap(~source)

#Valence
image_ratings_all %>%
  group_by(source) %>%
  ggplot(aes(x = valence_human, y = valence_ml)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ggtitle("Valence") +
  scale_x_continuous("Human Ratings", limits = c(1,9), n.breaks = 9) +
  scale_y_continuous("Machine Ratings", limits = c(1,9), n.breaks = 9) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  facet_wrap(~source)

#Valence and Arousal
image_ratings_all_long %>%
  group_by(source) %>%
  ggplot(aes(x = arousal, y = valence)) +
  geom_point() +
  geom_smooth(method = "lm") +
  ggtitle("Rating by Source and Raiter") +
  scale_x_continuous("Arousal", limits = c(1,9), n.breaks = 9) +
  scale_y_continuous("Valence", limits = c(1,9), n.breaks = 9) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  facet_wrap(~source + raiter)

```

## Av Participant Rating Across Images

Plot showing average participant ratings on valence and arousal across all images.

```{r av participant, warning=F, message=F}

#Valence
image_ratings_all %>%
  group_by(source) %>%
  ggplot() +
  geom_point(mapping = aes(x = reorder(image, valence_human), 
                           y = valence_human, color = source)) +
  ggtitle("Average Participant Valence Ratings Across Images") +
  xlab("Image") +
  scale_y_continuous("Valence", limits = c(1,9), n.breaks = 9) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

#Arousal
image_ratings_all %>%
  group_by(source) %>%
  ggplot() +
  geom_point(mapping = aes(x = reorder(image, arousal_human), 
                           y = arousal_human, color = source)) +
  ggtitle("Average Participant Arousal Ratings Across Images") +
  xlab("Image") +
  scale_y_continuous("Arousal", limits = c(1,9), n.breaks = 9) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank())

#Faceted
image_ratings_all_extralong %>%
  group_by(source) %>%
  ggplot() +
  geom_point(mapping = aes(x = reorder(image, value), 
                           y = value, color = source)) +
  ggtitle("Average Participant Ratings Across Images") +
  xlab("Image") +
  scale_y_continuous("Rating", limits = c(1,9), n.breaks = 9) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold")) +
  theme(axis.text.x=element_blank(),
        axis.ticks.x=element_blank()) +
  facet_wrap(~measure)

```

## Smartphone with Elipses

```{r smartphone elipses, warning=F, message=F}

#All by Rater
image_ratings_all_long %>%
  filter(source == "smartphone") %>%
  mutate(Raiter = ifelse(raiter == "human", "Human", "Machine")) %>%
  group_by(image) %>%
  ggplot(aes(x = arousal, y = valence, color = Raiter)) +
  geom_point(linewidth = 1.5) +
  scale_colour_manual("Ratings", values =
                        c("Human"="#1f77b4", "Machine"="#ff7f0e")) +
  stat_ellipse(linewidth = 1) +
  geom_line(aes(group = image), color="black", size = 0.2) +
  ggtitle("Valence and Arousal:\nSmartphone Images\n") +
  scale_x_continuous("Arousal", limits = c(1,9), n.breaks = 9) +
  scale_y_continuous("Valence", limits = c(1,9), n.breaks = 9) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        text = element_text(size = 16))

```

## Triangle Plot: OASIS

Plot displaying distance between participant, ML, and previous OASIS ratings on OASIS images.

```{r triangle OASIS, warning=F, message=F}

image_ratings_all %>%
  filter(source=="OASIS")%>%
  ggplot() +
  geom_point(mapping = aes(x = arousal_human, y = valence_human, 
                           colour = "Human"), size = 2) +
  stat_ellipse(mapping = aes(x = arousal_human, y = valence_human, 
                           colour = "Participant"), size = 1) +
  geom_point(mapping = aes(x = arousal_ml, y = valence_ml, 
                           colour = "Human"), size = 2) +
  stat_ellipse(mapping = aes(x = arousal_ml, y = valence_ml, 
                           colour = "Machine"),  size = 1) +
  geom_point(mapping = aes(x = adjusted_arousal, y = adjusted_valence, 
                           colour = "Prior OASIS"), size = 2) + 
  stat_ellipse(mapping = aes(x = adjusted_arousal, y = adjusted_valence, 
                           colour = "Prior OASIS"), size = 1) + 
  scale_colour_manual("Ratings", values = 
                        c("Human"="#1f77b4", 
                          "Machine"="#ff7f0e", 
                          "Prior OASIS"="#2ca02c")) +
  geom_segment(aes(x = arousal_human, y = valence_human, 
                   xend= arousal_ml, yend = valence_ml), 
               linetype = 1, size = 0.5, color ="black") +
  geom_segment(aes(x = arousal_ml, y = valence_ml,
                   xend = adjusted_arousal, yend = adjusted_valence), 
               linetype = 1, size = 0.5, color ="black") +
  geom_segment(aes(x = adjusted_arousal, y = adjusted_valence,
                   xend= arousal_human, yend = valence_human), 
               linetype = 1, size = 0.5, color ="black") +
  scale_x_continuous("Arousal", limits = c(1,9), n.breaks = 9) +
  scale_y_continuous("Valence", limits = c(-1,10), n.breaks = 11) +
  ggtitle("Participant, ML, and Previous \nOASIS Rating Relationships") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        text = element_text(size = 16))

```

# Valence & Arousal Data

## Data Overview

```{r human do, warning=F, message=F}

glimpse(image_ratings_human)

kbl(describe(image_ratings_human[,c(20:219)])) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), 
                full_width = F,
                fixed_thead = F)

#Stats
image_ratings_all %>%
  select(valence_human, valence_ml, adjusted_valence) %>%
  tbl_summary(
    label = list(valence_human ~"Human", valence_ml ~ "Machine", adjusted_valence ~ "OASIS Adjusted"),
    statistic = list(all_continuous() ~ "{min}-{max} ({mean}, {SD})"),
    missing = "ifany") %>%
  modify_header(label ~ "") %>%
  as_gt() %>%
  tab_header("Valence") 

image_ratings_all %>%
  select(arousal_human, arousal_ml, adjusted_arousal) %>%
  tbl_summary(label = list(arousal_human ~"Human", arousal_ml ~ "Machine", 
                           adjusted_arousal ~ "OASIS Adjusted"),
    statistic = list(all_continuous() ~ "{min}-{max} ({mean}, {SD})"),
    missing = "ifany") %>%
  modify_header(label ~ "") %>%
  as_gt() %>%
  tab_header("Arousal") 

#Stats by Source
image_ratings_all %>%
  select(source, valence_human, valence_ml) %>%
  tbl_summary(by = source, 
              label = list(valence_human ~"Human", valence_ml ~ "Machine"),
              statistic = list(all_continuous() ~ "{min}-{max} ({mean}, {SD})"),
              missing = "ifany") %>%
  modify_header(label ~ "") %>%
  as_gt() %>%
  tab_header("Valence") 

image_ratings_all %>%
  select(source, arousal_human, arousal_ml) %>%
  tbl_summary(by = source, 
              label = list(arousal_human ~"Human", arousal_ml ~ "Machine"),
              statistic = list(all_continuous() ~ "{min}-{max} ({mean}, {SD})"),
              missing = "ifany") %>%
  modify_header(label ~ "") %>%
  as_gt() %>%
  tab_header("Arousal") 

```

## Correlation Tests

Let's look at the correlation between the machine and human ratings for the 100 images.

```{r corr all images, warning=F, message=F}

# All Images
cor.test(image_ratings_all$valence_human, image_ratings_all$valence_ml)

cor.test(image_ratings_all$arousal_human, image_ratings_all$arousal_ml)

# Smartphone Only
cor.test(image_ratings_smartphone$valence_human, image_ratings_smartphone$valence_ml)

cor.test(image_ratings_smartphone$arousal_human, image_ratings_smartphone$arousal_ml)

cor.test(image_ratings_smartphone$arousal_human,image_ratings_smartphone$valence_human)

cor.test(image_ratings_smartphone$arousal_ml, image_ratings_smartphone$valence_ml)

# OASIS Only
cor.test(image_ratings_OASIS$valence_human, image_ratings_OASIS$valence_ml)

cor.test(image_ratings_OASIS$arousal_human, image_ratings_OASIS$arousal_ml)

cor.test(image_ratings_OASIS$arousal_human, image_ratings_OASIS$valence_human)

cor.test(image_ratings_OASIS$arousal_ml, image_ratings_OASIS$valence_ml)

#Adjusted Arousal vs Machine Arousal
cor.test(image_ratings_OASIS$adjusted_arousal, image_ratings_OASIS$arousal_ml)

#Adjusted Valence vs Machine Valence
cor.test(image_ratings_OASIS$adjusted_valence, image_ratings_OASIS$valence_ml)

#Adjusted Arousal vs Human 
cor.test(image_ratings_OASIS$adjusted_arousal, image_ratings_OASIS$arousal_human)

#Adjusted Valence vs Human
cor.test(image_ratings_OASIS$adjusted_valence, image_ratings_OASIS$valence_human)

```

## ICC

```{r ICC, message=F, warning=F}

#All Images Valence ICC
psych::ICC(image_ratings_all[,c("valence_human","valence_ml")])

#All Images Arousal ICC
psych::ICC(image_ratings_all[,c("arousal_human","arousal_ml")])

#Smartphone Valence ICC
psych::ICC(image_ratings_smartphone[,c("valence_human","valence_ml")])

#Smartphone Arousal ICC
psych::ICC(image_ratings_smartphone[,c("arousal_human","arousal_ml")])

#OASIS Valence ICC
psych::ICC(image_ratings_OASIS[,c("valence_human","valence_ml")])

#OASIS Arousal ICC
psych::ICC(image_ratings_OASIS[,c("arousal_human","arousal_ml")])

#OASIS Human Valence ICC
psych::ICC(image_ratings_OASIS[,c("valence_human", "adjusted_valence")])

#OASIS Human Arousal ICC
psych::ICC(image_ratings_OASIS[,c("arousal_human", "adjusted_arousal")])

```

## Lin's Correspondance Coefficient

```{r lin cc, warning=T, message=F}

#All Images Valence ICC
CCC(image_ratings_all$valence_human, image_ratings_all$valence_ml, 
    ci = "z-transform", conf.level = 0.95, na.rm = FALSE)

#All Images Arousal ICC
CCC(image_ratings_all$arousal_human, image_ratings_all$arousal_ml, 
    ci = "z-transform", conf.level = 0.95, na.rm = FALSE)

#Smartphone Valence ICC
CCC(image_ratings_smartphone$valence_human, image_ratings_smartphone$valence_ml, 
    ci = "z-transform", conf.level = 0.95, na.rm = FALSE)

#Smartphone Arousal ICC
CCC(image_ratings_smartphone$arousal_human, image_ratings_smartphone$arousal_ml, 
    ci = "z-transform", conf.level = 0.95, na.rm = FALSE)

#OASIS Valence ICC
CCC(image_ratings_OASIS$valence_human, image_ratings_OASIS$valence_ml, 
    ci = "z-transform", conf.level = 0.95, na.rm = FALSE)

#OASIS Arousal ICC
CCC(image_ratings_OASIS$arousal_human, image_ratings_OASIS$arousal_ml, 
    ci = "z-transform", conf.level = 0.95, na.rm = FALSE)

#OASIS Human Valence ICC
CCC(image_ratings_OASIS$valence_human, image_ratings_OASIS$adjusted_valence, 
    ci = "z-transform", conf.level = 0.95, na.rm = FALSE)

#OASIS Human Arousal ICC
CCC(image_ratings_OASIS$arousal_human, image_ratings_OASIS$adjusted_arousal, 
    ci = "z-transform", conf.level = 0.95, na.rm = FALSE)

```

## Means and SDs

```{r means SD, warning=F, message=F, echo=F}

#All Images
meanSD_rows_all <- c("Human" ,"Machine", "OASIS Adjusted", "Human" ,"Machine", "OASIS Adjusted")
mean_col_all <- c(mean(image_ratings_all$arousal_human), mean(image_ratings_all$arousal_ml), 
                  mean(image_ratings_all$adjusted_arousal, na.rm = TRUE),
                  mean(image_ratings_all$valence_human), mean(image_ratings_all$valence_ml), 
                  mean(image_ratings_all$adjusted_valence, na.rm = TRUE))
SD_col_all <- c(psych::SD(image_ratings_all$arousal_human), psych::SD(image_ratings_all$arousal_ml), 
                psych::SD(image_ratings_all$adjusted_arousal, na.rm = TRUE),
                psych::SD(image_ratings_all$valence_human), psych::SD(image_ratings_all$valence_ml), 
                psych::SD(image_ratings_all$adjusted_valence, na.rm = TRUE))

meanSD_table_all <- data.frame(meanSD_rows_all, mean_col_all, SD_col_all)

meanSD_table_all <- meanSD_table_all %>%
  rename(Raiting = meanSD_rows_all,
         Mean = mean_col_all,
         SD = SD_col_all)

kbl(meanSD_table_all, caption = "All Images") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = F) %>%
  pack_rows("Arousal", 1, 3) %>%
  pack_rows("Valence", 4, 6)

#By Source
meanSD_rows_bySource <- c("OASIS Human","OASIS Machine", "Smartphone Human" ,"Smartphone Machine",
                          "OASIS Human","OASIS Machine", "Smartphone Human" ,"Smartphone Machine")
mean_col_bySource <- c(mean(image_ratings_OASIS$arousal_human), 
                       mean(image_ratings_OASIS$arousal_ml), 
                       mean(image_ratings_smartphone$arousal_human), 
                       mean(image_ratings_smartphone$arousal_ml), 
                       mean(image_ratings_OASIS$valence_human), 
                       mean(image_ratings_OASIS$valence_ml), 
                       mean(image_ratings_smartphone$valence_human), 
                       mean(image_ratings_smartphone$valence_ml))
SD_col_bySource <- c(psych::SD(image_ratings_OASIS$arousal_human), 
                     psych::SD(image_ratings_OASIS$arousal_ml), 
                     psych::SD(image_ratings_smartphone$arousal_human), 
                     psych::SD(image_ratings_smartphone$arousal_ml), 
                     psych::SD(image_ratings_OASIS$valence_human), 
                     psych::SD(image_ratings_OASIS$valence_ml), 
                     psych::SD(image_ratings_smartphone$valence_human), 
                     psych::SD(image_ratings_smartphone$valence_ml))

meanSD_table_bySource <- data.frame(meanSD_rows_bySource, mean_col_bySource, SD_col_bySource)

meanSD_table_bySource <- meanSD_table_bySource %>%
  rename(Raiting = meanSD_rows_bySource,
         Mean = mean_col_bySource,
         SD = SD_col_bySource)

kbl(meanSD_table_bySource, caption = "By Images Source") %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = F) %>%
  pack_rows("Arousal", 1, 4) %>%
  pack_rows("Valence", 5, 8)

```

# Day In the Life Deep Affect Module

## Data Overview

```{r DAM data, warning=F, message=F}

glimpse(image_ratings_DITL)

kbl(describe(image_ratings_DITL[,c(2,3:4)])) %>%
  kable_styling(bootstrap_options = c("striped", "hover"), full_width = F)

```

## Plots

```{r DAM plots, warning=F, message=F}

#By Order
image_ratings_DITL_long %>%
  ggplot(aes(x = row_id, y = value, col = rating)) +
  geom_point(aes(color = rating)) +
  geom_line(aes(color = rating)) +
  ggtitle("Deep Affect Module: By Order") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

#By Order with subset highlighted
image_ratings_DITL %>%
  ggplot(aes(x=row_id)) +
  geom_rect(xmin = 375, xmax = 1000, ymin = 0, ymax= 7, 
            fill = "grey90", alpha = 0.03) +
  geom_line(aes(y=valence), color = "blue", alpha = 0.5) +
  geom_line(aes(y=arousal), color = "red", alpha = 0.75) +
  ggtitle("Deep Affect Module: By Order") +
  scale_y_continuous(name = "Score") +
  scale_x_continuous(name = "Screenshot", n.breaks = 10) +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"),
        text = element_text(size = 16))

```
